Compression of interferometric radio-astronomical data

### 2013-04-05 articles/Article-compression/compression.tex
Work on compr art

\section{Background}
% up to 500 words of referenced text expanding on the background to the work (some overlap with the summary is acceptable), before proceeding to a concise, focused account of the findings, ending with one or two short paragraphs of discussion.
Unprocessed data from interferometric radio observatories consists of correlated signals from all the pairs of antennas that are part of the interferometric array. These correlated signals are measured in many spectral channels, and integrated over short timesteps before they are recorded to disk \cite{thompson-radio-interferometry}.

>>>>

\section{Background}
% up to 500 words of referenced text expanding on the background to the work (some overlap with the summary is acceptable), before proceeding to a concise, focused account of the findings, ending with one or two short paragraphs of discussion.
Unprocessed data from interferometric radio observatories consists of correlated signals from all the pairs of antennas that are part of the interferometric array. These correlated signals are measured in spectral channels, and integrated over short timesteps before they are recorded to disk \cite{thompson-radio-interferometry}.
